---
title: "Untitled"
author: "Esther Kyeremah"
date: "2023-09-22"
output: github_document
---

```{r message = FALSE}

library("moderndive")
library('tidyverse')
data("early_january_weather")

```


The variables are option, temp, year, month, day, hour, dewp, humid, wind_dir, wind_speed, wind_gust, precip, pressure, visib, time_hour.... There are `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns. 

```{r q1a, echo =FALSE, message = FALSE}

mean(pull(early_january_weather, temp))

```


The mean temperature is `r mean(pull(early_january_weather, temp))`.

```{r q1b, echo = FALSE, message = FALSE}


ggplot (early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()

ggsave("scatterplot_time_temp.pdf")
```

The pattern in the scatterplot is undulating showing a rise and fall in the temperature over the days.

*Problem 2*
```{r}

data_frame =
 tibble(rand_samp = rnorm(10, mean = 0),
   log_vec = rand_samp > -0,
   char_vec = c("My", "name", "is", "Esther", "and", "I", "am", "a", "master", "student"),
   factor_vec = factor(c("low", "low", "moderate", "high", "moderate", "moderate", "moderate", "high", "high", "high"))
   )
   
 
```

*Problem 3*
```{r}
mean(pull(data_frame,rand_samp))

mean(pull(data_frame, log_vec))

mean(pull(data_frame, char_vec))

mean(pull(data_frame, factor_vec))

```
The mean for the random sample is `r mean(pull(data_frame,rand_samp))` and the mean for the logical vector is `r mean(pull(data_frame, log_vec)) `For the character and vector factors we didnt get any answers because they are not numeric or logical.


```{r}
mean(as.numeric(pull(data_frame, log_vec)))
mean(as.numeric(pull(data_frame, char_vec)))
mean(as.numeric(pull(data_frame, factor_vec)))

```

The character vector still doesnt give a numeric as they are just characters. The factor is however a 3-level variable so each level has been converted to a number.


